Results

### 2025-12-01 notebooks/000_data.qmd
chore: cleanup ipynb

>>>>

## Anisotropy Data

# Anisotropy

- PSP_SWP_SPI_SF00_L3_MOM

    - Notes: Partial moments of the Proton distribution function in the SPAN-Ion instrument, PSP spacecraft, and RTN coordinate systems. User should be aware that the full ion distribution is typically NOT in the FOV of the instrument.

    - `T_TENSOR`  Partial Moment Temperature Tensor in instrument frame

- WI_H0_SWE

    - `Te_anisotropy`	Temperature anisotropy = Te_para / Te_perp

- WI_PLSP_3DP

    - `MOM.P.MAGT3`	---> [P.SYMM_MAGT3] Proton temperature tensor... rotated into a field-aligned coordinate basis and then taking the diagonal elements only

- WI_ELM2_3DP : Wind 3dp, PESA Low (~24 sec resolution) energy spectra with ion moments

    - `MAGT3`	---> [MAGT3] electron temperature tensor... rotated into a field-aligned coordinate basis and then taking the diagonal elements only

- THB_L2_ESA

    - `thb_peeb_magt3Q`	-----Electron Temperature, Field Aligned (Tprp1FA, Tprp2FA, TparFA)

    - `thb_peef_magt3Q`	-----Electron Temperature, Field Aligned (Tprp1FA, Tprp2FA, TparFA)

    - `thb_peif_magt3Q`	-----Temperature, Field Aligned (TprpFA1, TprpFA2, TparFA)

- THB_L2_MOM

    - `thb_peem_ptens_magQ`	-----Electron Pressure Tensor, Field Aligned

    - `thb_peem_t3_magQ`	-----Electron Temperature, Field Aligned (TprpFA1, TprpFA2, TparFA)

    - `thb_peim_ptens_magQ`	-----Ion Pressure Tensor, Field Aligned

    - `thb_peim_t3_magQ`	-----Ion Temperature, Field Aligned (TprpFA1, TprpFA2, TparFA)
